<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Managing your NAMESPACE}
-->


```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  error = FALSE,
  tidy = FALSE
)
```

---
title: "Package overview"
author: "Janko Thyson"
date: "Thursday, September 25, 2014"
output: pdf_document
---

## Main top-level functions


### `ensureRappRuntime()`

- calls `initializeRappOptions()` and thus ensures an environment that contains all options (in `options(".rapp")` or `getOption(".rapp")`)
  
```{r}
initializeRappOptions()
ls(getOption(".rapp")$.rte, all.names = TRUE)
```

- Reads runtime options from `/options/options_runtime.r` if exists

- Ensures global directory and sets respective option (`global_dir`): `setGlobalDirectory()` and `ensureGlobalDirectory()`

- Ensures internal repositories and sets respective options (`repos_global`, `repos_pkgs`, `repos_root`): `setInternalRepositories()`

- Sets option for runtime mode (`runtime_mode`): `setRuntimeMode()`

- Sets package library to use (option `lib` and in `.libPaths()`): `setLibrary()`

- Ensures the existence of all necessary project components in the packageprojects root directory: `ensureProjectComponents()` and `ensureRappComponents()`

- If called from the context of a package project or if an option file `/options/options_ns.r` exists, then these options are read (`readRappOptionFile()`) and merged into the option container `getOption(".rapp")`. 

  To be more specific, a subcontainer is created where these options are stored. The name of the subcontainer corresponds to the name of the package project or the application (`mergeNamespaceRappOptions()`)

